Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-24 paper/paper.tex
pass on section 4

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[trim=0 350 100 0,clip,width=0.65\textwidth]{figs/nids-workflow}
  \caption{\tname\ workflow.}
  \label{fig:overview}
  \vspace{-1ex}
\end{figure*}

@@

\vspace{1ex}
\noindent\textbf{Overview.}~To create rules, \tname\ leverages (1)
benign and malicious network traffic and (2) rules from public
rulesets. \tname\ takes on input malicious and benign traffic and a
set of rules from public rulesets and produces on output a list of
plausible rules to isolate the malicious from the benign
traffic. Figure~\ref{fig:overview} shows the workflow of \tname{} as a
pipeline of three components, which appear numbered in the figure.
The inputs of the technique appear at the bottom of the figure whereas
the output appears at the right.

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, provided on
input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects rule options directly from the input messages (see
Section~\ref{sec:rules-and-packets}). As only malicious traffic is
considered in this step, the rule produced is likely overspecified,
\ie{}, it includes more options than the golden rule (see
Section~\ref{sec:suri-metas-coverage}). Consequently, the use of that
rule could lead to false negatives as not all manifestations of the
same attack are identical. Second, \tname{} generates plausible rules
that are similar to the seed rule produced in the previous step. It is
worth noting that any subset of the original set of options captures
the malicious traffic. \tname{} leverages that observation to search
for rules containing a proper subset of rules defined in the original
seed option. As the generation procedure discards options from the
initial rule, the rules \tname{} creates satisfies the property of
capturing malicious traffic. However, the goal of \tname\ is to
produce rules that capture \emph{only} malicious traffic. To achieve
that goal, \tname{} uses benign traffic to reduce the likelihood the
\nids\ will report false positives on the synthesized rule. The
minimization step uses a population-based gradient descent-like search
to find all plausible rules derived from the seed rule, obtained in
the previous step. Third, \tname{} uses several heuristic functions
derived from a data set of rules to rank the rules generated in the
previous step.

@@

>>>>

\begin{figure*}[ht]
  \centering
  \includegraphics[trim=0 395 50 0,clip,width=0.65\textwidth]{figs/nids-workflow}
  \caption{\tname\ workflow.}
  \label{fig:overview}
  \vspace{-2ex}
\end{figure*}

@@

@@

\vspace{1ex}
\noindent\textbf{Overview.}~To create rules, \tname\ leverages (1)
benign and malicious network traffic and (2) rules from public
rulesets. \tname\ takes on input malicious and benign traffic and a
set of rules from public rulesets and produces on output a list of
\emph{plausible rules}---\ie{}, rules that isolate the malicious
traffic from the benign traffic---in order of their likelihood to
reflect user's intent. Figure~\ref{fig:overview} shows the workflow of
\tname{} as a pipeline of three components, which appear numbered in
the figure.  Public data sets of benign
traffic~\cite{tcpreplay,stratosphere-normal} and \nids\ rules
exist~\cite{emerging-threats-open}. Consequently, a user of \tname{}
only needs to provide the malicious traffic on input.

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, which is
provided on input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects rule options directly from the input messages (see
Section~\ref{sec:rules-and-packets}). As only malicious traffic is
considered in this step, the rule produced is likely overspecified,
\ie{}, it may be more restrictive than the golden rule (see
Section~\ref{sec:suri-metas-coverage}). Consequently, the use of that
rule could lead to false negatives. Second, \tname{} generates rules
that weakens the constraints expressed in the inferred seed rule
whilest still capturing the malicious traffic. Given that every option
declared in a rule needs to be satisfied for a rule to capture an
attack, any subset of the set of options---inferred in the first
step---captures the malicious traffic by definition. \tname{}
leverages that observation to search for rules containing a proper
subset of rules defined in the original seed option. Although that
approach captures the malicious traffic, it can result in false
positives. Intuitively, there are no restrictions on to what extent a
rule can be relaxed. \tname{} uses benign traffic for that
purpose. The minimization step uses a population-based gradient
descent-like search to find all plausible rules derived from the seed
rule, obtained in the previous step. Finally, \tname{} uses several
heuristic functions derived from a data set of existing rules to rank
the plausible rules generated in the previous step.

%%  As the generation
%% procedure discards options from the initial rule, the rules \tname{}
%% creates satisfy the property of capturing malicious traffic.

@@

\Mar{----------------------------------- PAREI AQUI}
